Algorithms for Estimating Trends in Global Temperature Volatility

### 2018-09-04 aaai-2018/khodadadi-mcdonald-aaai19.tex
update paper

though it uses a different likelihood
function to emphasize variance estimation rather than trends in mean
signal. Furthermore, the focus is in high-dimensional, regular data
rather than a small number of changing graphs.

@@

\begin{figure}[tb]
  \centering	
  \includegraphics[height=.15\textheight]{Figures/true_var_spatial}\\
  \includegraphics[height=.15\textheight]{Figures/true_fitted_var}
  \caption{Top: Variance function at $t=25$ (left) and $t=45$
    (right). Bottom: The true (orange) and estimated standard deviation 
    function at the location (0,0). The estimated values are
    obtained using linearized ADMM with $\lambda_s=0.1$ and two
    values of $\lambda_t$: $\lambda_t=5$ (blue) and
    $\lambda_t=100$ (green).} \label{fig:true_var_spatial}
\end{figure}

@@

\begin{figure}[tb]
  \centering	
  \includegraphics[height=.12\textheight]{Figures/true_fitted_var}
  \includegraphics[height=.12\textheight]{Figures/convergence}  
  \includegraphics[height=.12\textheight]{Figures/modelComp_MAE}  
  \caption{Left: The true (orange) and estimated standard deviation 
    function at the location (0,0). The estimated values are
    obtained using linearized ADMM with $\lambda_s=0.1$ and two
    values of $\lambda_t$: $\lambda_t=5$ (blue) and
    $\lambda_t=100$ (green). Middle: Convergence speed of linearized
    and consensus ADMM. Right: MAE for four models: admm\_opt: the
    proposed model with optimal values of $\lambda_t$ and $\lambda_s$,
    admm\_temp: no spatial penalty, admm\_sp: no temporal
    penalty.\attn{Fix these}} \label{fig:true_fitted_var}
\end{figure}

@@

\autoref{fig:cities_ts} shows the time-series of the 
temperature of three cities: Indianapolis (USA), San Diego (USA) and
Manaus (Brazil). The time-series of Indianapolis and San Diego show
clear cyclic behavior, though the amplitude of the cycles
changes. The time-series of Manaus does not
show any regular cyclic behavior. For this reason, we
first apply trend filtering to remove seasonal terms and de-trend
every time series. For each time-series, we found the optimal value of
the penalty parameter using \textit{k-fold cross-validation} with
$k=5$. We used the R package \textbf{genlasso} to perform these
computations \cite{arnold_efficient_2016}.  
\begin{figure}[tb]
	\centering
	\includegraphics[width=.2\textheight]{Figures/cities_ts}
 	\caption{Time-series of the temperature (in Kelvin) of three cities.}
 	\label{fig:cities_ts}
\end{figure} 
The blue curve in the left panel of Figure
\autoref{fig:bloom_estimatedSD} shows the time-series of the
temperature of Indianapolis after detrending using this method.

@@

\begin{figure}[tb]
  \centering
  \includegraphics[width=1\columnwidth]{Figures/ts_estimatedVar}
  \caption{Detrended data and the estimated SD for
    a small midwestern city (left) and San Diego (right).\attn{Fix these}} 
  \label{fig:avg_change_estimatedSD}
\end{figure}

>>>>

@@

\begin{figure}[tb]
  \centering	
  \includegraphics[height=.15\textheight]{Figures/true_var_spatial}\\
  \includegraphics[height=.2\textheight]{Figures/true_fitted_var}
  \caption{Top: Variance function at $t=25$ (left) and $t=45$
    (right). Bottom: The true (orange) and estimated standard deviation 
    function at the location (0,0). The estimated values are
    obtained using linearized ADMM with $\lambda_s=0.1$ and two
    values of $\lambda_t$: $\lambda_t=5$ (blue) and
    $\lambda_t=100$ (green).} \label{fig:true_var_spatial}
\end{figure}

@@

\begin{figure}[tb]
  \centering	
  \includegraphics[height=.16\textheight]{Figures/convergence}  
  \includegraphics[height=.16\textheight]{Figures/modelComp_MAE}  
  \caption{Top: Convergence speed of linearized
    and consensus ADMM. Bottom: MAE for four models: admm\_opt: the
    proposed model with optimal values of $\lambda_t$ and $\lambda_s$,
    admm\_temp: no spatial penalty, admm\_sp: no temporal
    penalty.\attn{Fix these}} \label{fig:true_fitted_var}
\end{figure}

@@

\autoref{fig:cities_ts} shows the time-series of the 
temperature of three cities: Indianapolis (USA), San Diego (USA) and
Manaus (Brazil). The time-series of Indianapolis and San Diego show
clear cyclic behavior, though the amplitude of the cycles
changes. The time-series of Manaus does not
show any regular cyclic behavior. For this reason, we
first apply trend filtering to remove seasonal terms and de-trend
every time series. For each time-series, we found the optimal value of
the penalty parameter using \textit{k-fold cross-validation} with
$k=5$. We used the R package \textbf{genlasso} to perform these
computations \cite{arnold_efficient_2016}.  
\begin{figure}[tb]
	\centering
	\includegraphics[width=.3\textheight]{Figures/cities_ts}
 	\caption{Time-series of the temperature (in Kelvin) of three cities.}
 	\label{fig:cities_ts}
\end{figure} 
The blue curve in the left panel of Figure
\autoref{fig:bloom_estimatedSD} shows the time-series of the
temperature of Indianapolis after detrending using this method.

@@

\begin{figure}[tb]
  \centering
  \includegraphics[width=1.1\columnwidth]{Figures/ts_estimatedVar}
  \caption{Detrended data and the estimated SD for
    a small midwestern city (left) and San Diego (right).\attn{Fix these}} 
  \label{fig:avg_change_estimatedSD}
\end{figure}
